FTLR proof cases

### 2018-06-29 fully-abstract-comp/ftlr-proof-cases.tex
Discharge two TODOs.
Proof of split lemma.

\begin{lemma}[Capability splitting retains safety for normal capabilities]
  \label{lem:splitting-safety-normal}
  If
  \begin{itemize}
  \item $\npair{(c,c)} \in \lrvg{\trust}(W)$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $b \le n \le e$
  \item $c_1 = ((\perm,\lin),\baddr,n,\aaddr)$
  \item $c_2 = ((\perm,\lin),n,\eaddr,\aaddr)$
  \item $c_3 = \linCons{c}$
  \end{itemize}
  then there exist $W_1,W_2$,$W_3$ such that
  \begin{itemize}
  \item $W = W_1 \oplus W_2 \oplus W_3$
  \item $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$
  \item $\npair{(c_3,c_3)} \in \lrvg{\trust}(W_3)$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO

  From $\npair{(c,c)} \in \lrvg{\trust}(W)$, we get that either $\perm = \noperm$, in which case we can pick the ownership distribution to be the same as before, or $\npair{[\baddr,\eaddr]} \in \readCond{\linear,R_R(r_3)}$.

    In the latter case, we get $S \subseteq \addressable{\linear,R_R(r_3)}$ and $R : S \fun \powerset{R_R(r_3)}$ such that $\forall r \in S \ldotp |R(r)| = 1$ and $\biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr]$.

    This gives us a way to distribute the ownership, namely $r_3$ gives up ownership of regions $R^{-1}([\baddr,\eaddr])$, $r_1$ gets ownership of $R^{-1}([\baddr,n])$, and $r_2$ gets ownership over $R^{-1}([n+1,\eaddr])$.
    The remainder of the ownership distribution remains unchanged.

TODO TODO TODO     
    Now we have to argue the following:
    \begin{itemize}
    \item if $\perm \in \readAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,n]} \in \readCond{\linear,R_R'(r_1)}$
      \item $\npair{[n+1,\eaddr]} \in \readCond{R_R'(r_2)}$
      \end{itemize}

    \item if $\perm \in \writeAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,n]} \in \writeCond{\linear,R_R'(r_1)}$
      \item $\npair{[n+1,\eaddr]} \in \writeCond{\linear,R_R'(r_2)}$
      \end{itemize}
    \item $\perm \neq \rx$

      Assuming $\perm = \rx$, then it must have been the case that $\lin = \normal$ contradicting the assumption $\isLinear{(\Phi_S(r_3))}$.

    \end{itemize}
    or
    \begin{itemize}
    \item 
    \end{itemize}
    depending on whether the permission of the capability was $\perm = \noperm$
    or not. In both cases, the result follows immediately by the assumptions.

    If $\neg \isLinear{(\Phi_S(r_3))}$, then we pick $R_R' = R_R$

    TODO

\end{proof}

@@

\begin{lemma}
  \label{lem:sealed-lrv-lrexj}
  If
  \begin{itemize}
  \item $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$
  \item $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$ 
  \item $\nonExec{\vsc_1'}$ and $\nonExec{\vsc_2'}$
  \item $W_{R,1} \oplus W_{R,2} \oplus W_M$ is defined
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$
  \end{itemize}
  Then
  \begin{itemize}
  \item $\npair{(\vsc_1,\vsc_2,\vsc_1',\vsc_2')} \in \lrexj(W_{R,1}\oplus W_{R,2})$
  \end{itemize}
\end{lemma}
\begin{proof}
  From $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$, we know that
  \begin{itemize}
  \item $(\isLinear{\src{\vsc_1}} \text{ iff } \isLinear{\vsc_1'})$ 
  \item $\exists r \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp$ 
  \item $\pwheap[W_{R,1}](r) = (\pure,\_,H_\sigma)$ 
  \item $H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc$
  \item $\npair[n']{\stpair[.]{\vsc_1}{\vsc_1'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,1})$ for all $n' < n$
  \item If $(\isLinear{\src{\vsc_1}}$ then for all $W' \future W_{R,1}$, $W_o$, $n' < n$, $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o)$, we have that
    \begin{equation*}
      \npair[n']{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W'\oplus W_o))
    \end{equation*}
  \item If $(\nonLinear{\src{\vsc_1}}$ then for all $W' \future \purePart{W_{R,1}}$, $W_o$, $n' < n$, $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o)$, we have that
    \begin{equation*}
      \npair[n']{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W'\oplus W_o))
    \end{equation*}
  \end{itemize}

  From $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$, we know that
  \begin{itemize}
  \item $(\isLinear{\src{\vsc_2}} \text{ iff } \isLinear{\vsc_2'})$ 
  \item $\exists r' \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp$ 
  \item $\pwheap[W_{R,2}](r') = (\pure,\_,H_\sigma)$ 
  \item $H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc$
  \item $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$ for all $n' < n$
  \end{itemize}

  From $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$, we know that two different regions cannot have $H_\sigma$ defined for the same $\sigma$, so that $r = r'$.
  Both when $\isLinear{\vsc_1}$ and when $\nonLinear{\vsc_1}$ (using Lemma~\ref{lem:world-fut-purePart}), we know that for all $W' \future W_{R,1}$, $W_o$, $n' < n$, $\vsc_2$, $\vsc_2'$, $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o)$, we have that
  \begin{equation*}
    \npair[n']{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W'\oplus W_o))
  \end{equation*}
  We can now instantiate this fact with $W' = W_{R,1}$, $W_o = W_{R,2}$, $n' = n-1$, and the fact that $\npair[n-1]{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$ (see above) to conclude
  \begin{equation*}
    \npair[n-1]{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W_{R,1}\oplus W_{R,2})\text{.}
  \end{equation*}
\end{proof}

>>>>

\begin{lemma}[Capability splitting retains safety for normal capabilities]
  \label{lem:splitting-safety-normal}
  If
  \begin{itemize}
  \item $\npair{(c,c)} \in \lrvg{\trust}(W)$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $b \le s < e$
  \item $c_1 = ((\perm,\lin),\baddr,s,\aaddr)$
  \item $c_2 = ((\perm,\lin),s+1,\eaddr,\aaddr)$
  \item $c_3 = \linCons{c}$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W \oplus \purePart{W_1 \oplus W_2 \oplus W_3}}$
  \end{itemize}
  then there exist $W_1,W_2$,$W_3$ such that
  \begin{itemize}
  \item $W = W_1 \oplus W_2 \oplus W_3$
  \item $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$
  \item $\npair{(c_3,c_3)} \in \lrvg{\trust}(W_3)$
  \end{itemize}
\end{lemma}
\begin{proof}

  If $\lin = \normal$, then we pick $W_3 = W$ and $W_1 = W_2 = \purePart{W_3}$ which easily satisfies $W = W_1 \oplus W_2 \oplus W_3$.

  Assuming $\gc = (\ta,\gc,\gsigrets,\gsigcloss)$, we know by assumption $\npair{(c,c)} \in \lrvg{\trust}(W)$ that either
\begin{itemize}
\item $\ta \subseteq [\baddr,\eaddr]$; or
\item $\ta \# [\addr,\eaddr]$
\end{itemize}
In the former case, the result follows from Lemma~\ref{lem:non-linear-pure} and Lemma~\ref{lem:conds-shrinkable}.

In the latter case, we know that $[\baddr,s],[s+1,\eaddr] \neq \emptyset$ because $b \le s < e$, so the result follows from Lemma~\ref{lem:non-linear-pure} and Lemma~\ref{lem:conds-shrinkable}.

If $\lin = \linear$, then 
we know from $\npair{(c,c)} \in \lrvg{\trust}(W)$ and w.l.o.g we can assume
\begin{itemize}
\item $\npair{[\baddr,\eaddr]} \in \readCond{\linear,W}$
\item $\npair{[\baddr,\eaddr]} \in \writeCond{\linear,W}$
\end{itemize}
from this, we get $S_{\var{read}} \subseteq \addressable{\linear,\pwheap{W}}$ and
$R_{\var{read}} : S_{\var{read}} \fun \Worlds$ such that
\begin{itemize}
\item $\biguplus_{r\in S_{\var{read}}} R_{\var{read}}(r) \supseteq A$
\item $\forall r\ldotp |R_{\var{read}}(r)|  = 1$
\item $\forall r \in S_{\var{read}} \ldotp \pwheap(r).H \nsubeq \stdreg{R_{\var{read}}(r),\gc}{\pur}.H$
\end{itemize}
and
$S_{\var{write}} \subseteq \addressable{\linear,\pwheap{W}}$ and
$R_{\var{write}} : S_{\var{write}} \fun \Worlds$ such that
\begin{itemize}
\item $\biguplus_{r\in S_{\var{write}}} R_{\var{write}}(r) \supseteq A$
\item $\forall r\ldotp |R_{\var{write}}(r)|  = 1$
\item $\forall r \in S_{\var{write}} \ldotp \pwheap(r).H \nsupeq
  \stdreg{R_{\var{write}}(r),\gc}{\pur}.H \wedge \pwheap(r) \text{ is address-stratified}$
\end{itemize}

Now we would like to show $R_{\var{read}}^{-1}([\baddr,\eaddr]) = R_{\var{write}}^{-1}([\baddr,\eaddr])$.
We know that the two sets are the same size as both $R$'s map to singleton sets.
This means that there exists $r \neq r'$ s.t.\ $R_{\var{read}}(r) =
R_{\var{write}}(r') = \{\aaddr'\}$ for $\aaddr' \in [\baddr,\eaddr]$.

By definition of the standard region, we know that for any $\hat{W}$ and any $\ms$ and $\ms'$ where $\npair[n-1]{(\ms,\ms')} \in \pwheap(r)$ we have $\dom(\ms)= \dom(\ms') = \{a'\}$.

By assumption $\pwheap(r)$ is address-stratified which means that for any $\hat{W}$ and any $\ms$ and $\ms'$ where $\npair[n-1]{(\ms,\ms')} \in \pwheap(r)$ we have $\dom(\ms)e= \dom(\ms') = \{a'\}$.

By the memory satisfaction, the memory must be split into disjointed parts that
each satisfy a region. With two regions that require a memory segment pair with
the same domain, we cannot satisfy all the regions, so we must have

Now pick $W_1$ as the world that owns $R_{\var{read}}^{-1}([\baddr,s])$, $W_2$
the world that owns $R_{\var{read}}^{-1}([s+1,\eaddr])$, and $W_3$ as the world
that owns the remaining regions of $W$.

It is clearly the case that $W = W_1 \oplus W_2 \oplus W_3$.

In this case, we need to show
\[
  \npair{(0,0)} \in \lrvg{\trust}(W_3)
\]
which is trivially the case.

For the remaining, it suffices to show
\begin{itemize}
\item $\npair{[\baddr,s]} \in \readCond{\linear,W_1}$
\item $\npair{[\baddr,s]} \in \writeCond{\linear,W_1}$
\item $\npair{[s+1,\eaddr]} \in \readCond{\linear,W_2}$
\item $\npair{[s+1,\eaddr]} \in \writeCond{\linear,W_2}$
\end{itemize}
which follows by assumption.
\end{proof}

@@

\begin{lemma}
  \label{lem:sealed-lrv-lrexj}
  If
  \begin{itemize}
  \item $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$
  \item $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$ 
  \item $\nonExec{\vsc_1'}$ and $\nonExec{\vsc_2'}$
  \item $W_{R,1} \oplus W_{R,2}$ is defined
  \end{itemize}
  Then
  \begin{itemize}
  \item $\npair{(\vsc_1,\vsc_2,\vsc_1',\vsc_2')} \in \lrexj(W_{R,1}\oplus W_{R,2})$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}
